Modelling at-bats in baseball using the generalised Pareto distribution

### 2023-07-07 bibat/examples/baseball/docs/report.qmd

```{.python include="../baseball/data_preparation.py" start-line=77 end-line=161}
```

@@

```{.python include="../baseball/data_preparation.py" start-line=35 end-line=54}
```

>>>>

```{.python include="../baseball/data_preparation.py" start-line=78 end-line=162}
```

@@

```{.python include="../baseball/data_preparation.py" start-line=36 end-line=56}
```
